Lake Photic Zone Temperature across the Conterminous United States

### 2019-09-05 manuscript/manuscript.Rmd
small edits to MS

In summary, the main goal of this work was to develop a simple yet robust lake photic temperature model for all lakes in the conterminous US while still capturing key drivers of near-surface lake temperature. Additionally, this work (something about open science and GitHub link).

>>>>

To summarize, the main goal of this work was to develop a simple yet robust lake photic temperature model for all lakes in the conterminous US that capture key drivers of near-surface lake temperature. Additionally, this work (something about open science and GitHub link).
